Demand Forecasting of individual Probability Density Functions with Machine Learning

### 2020-08-14 LaTex/paper.tex
some more explanations and cosmetics

\newcommand{\fig}{Fig. }
\newcommand{\eqn}{Eqn. }
\newcommand{\tab}{Tab. }
\newcommand{\wrt}{w.r.t. }
\newcommand{\etal}{ {\em et al. }}

@@

In detail, the following meta-algorithm describes how the model parameters $f^k_j$ are obtained from the training data:
\begin{enumerate}
\item{Calculate the global average $\mu$ from all observed $y$ across all bins $k$ and features $j$.}
\item{Initialize the factors $f^k_j \leftarrow 1$}
\item{Cyclically iterate through features $j = 1,...,p $ and calculate in turn for each bin $k$ the partial factors $g$ and corresponding aggregated factors $f$, where indices $t$ (current iteration) and $\tau$ (current or preceding iteration) refer to iterations of full feature cycles as the training of the algorithm progresses:
\begin{equation} \label{factors}
g^k_{j,t} = \frac{\sum \limits_{x_{j,i} \in b^k_j} y_i}{\sum \limits_{x_{j,i} \in b^k_j} \hat{y}_{i,\tau}}\;\; \mathrm{where} \; \; f^k_{j,t} = \prod \limits_{s=1}^t g^k_{j,s}
\end{equation}
Here,  $g$ is a factor that is multiplied to $f_{t-1}$ in each iteration. The current prediction, $\hat{y}_\tau$, is calculated according to eqn. \ref{eqn:cb} with the current values of the aggregated factors $f$:
\begin{equation} \label{factors3}
\hat{y}_{i,\tau} = \mu \cdot \prod \limits_{j=1}^p f^k_{j,\tau}
\end{equation}
To be precise, the determination of $g^k_{j,t}$ for a specific feature $j$ uses $f^k_{j,t-1}$ in the calculation of $\hat{y}$. For the factors of all other features, the newest available values are used, i.e., depending on the sequence of features in the algorithm, either from the current ($\tau=t$) or the preceding iteration ($\tau=t-1$).}
\item{Quit when stopping criteria, e.g. the maximum number of iterations or no further improvement of an error metric such as the mean absolute deviation (MAD) or mean squared error (MSE), are met at the end of a full feature cycle.}
\end{enumerate}

@@

In case of discrete probability functions, such as the negative binomial function, the same argument still holds, but the definition of the inverse quantile function is replaced by the generalized inverse: $F^{-1}(y) = \mathrm{\inf \left \{x : F(x)>y\right  \} }$ for $y \in [0,1]$, see e.g. \cite[p. 54]{casella2002statistical}. In order to obtain a uniform distribution for discrete PDFs that is comparable to the case of continuous distributions, the histogram holding the inverse quantiles or values of the CDF is filled using random numbers according to the intervals of the CDF. For example, if the sales of zero items accounts for 75\% of the observed sales distribution for this item, the value of the CDF function that is used to fill the histogram is randomly chosen in the interval $[0,0.75]$. Proceeding similarly for all other observed values, the resulting histogram of CDF values should again be uniform as in the case of a continuous PDF.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{../figures/CDFHistos_uniform} \includegraphics[scale=0.4]{../figures/CDFHistos_broad} \includegraphics[scale=0.4]{../figures/CDFHistos_narrow} \includegraphics[scale=0.4]{../figures/CDFHistos_over} \includegraphics[scale=0.4]{../figures/CDFHistos_under}
\caption{\label{fig:cdf_histos} Quantile distribution for different cases of estimating the full probability distribution compared to the expected distribution:
correct prediction (``uniform''), variance overestimated (``broad''), variance underestimated (``narrow''), mean overestimated (``over''), mean underestimated (``under'')}
\end{center}
\end{figure}

@@

Then we compare the actual observed sales value (corrected for censored data if necessary) to different quantiles of the corresponding predicted distribution for each data record and average over a larger data sample. For example, if we wanted to check that the median of the distribution, corresponding to the $0.5$ quantile, is predicted correctly by the machine learning model, we would compare the quantile value $0.5$ to the ratio of quantile values of observed sales records being lower/higher than $0.5$. In other words, in case of the median, 50\% of the ex post observed target values should be observed below the median of the corresponding individual predicted PDF and 50\% above.

@@

In summary, this approach has two major benefits compared to the method discussed in sec. \ref{sec:cdf_histo}: First, by explicitly visualizing several different quantiles, the quantile profile plot reveals which part of the predicted PDF, such as the tails of the probability distribution, are particularly problematic. Second, by showing the dependency from the (arbitrary) variable on the x-axis, the quantile profile plot reveals deviations of the predicted PDF from the actuals for different parts, e.g. specific categories, of that variable. Two examples for this can be found in figures \ref{fig:invquant_mean} and \ref{fig:invquant_dayofweek} in the next section.

@@

We use data from a Kaggle online competition about estimating unit sales of Walmart retail goods \cite{kaggle_data} to demonstrate forecasting of demand for different product-location-date combinations in form of full individual PDFs by means of Cyclic Boosting and subsequent qualitative and quantitative evaluation of the PDF predictions. The fields identifying a unique sample of the data set are store (\texttt{store\_id}) and item identifiers (\texttt{item\_id}) as well as date. The target $y$ which we need to predict is the number of sales of a given product in a given store on a specific day, denoted by \texttt{sales}. In the following, we use data from 2013-01-01 to 2016-05-22, that describe the sales of 100 different products (\texttt{FOODS\_3\_500}, ..., \texttt{FOODS\_3\_599}) of the department \texttt{FOODS\_3} in 10 stores. All data before 2016 are used as the training data and the data from 2016 are used as an independent test or validation set. Besides the fields used to identify an individual sales record and the corresponding observed sales value, namely \texttt{item\_id}, \texttt{store\_id}, \texttt{date}, \texttt{sales}, we also use the fields \texttt{event\_name\_1}, \texttt{event\_type\_1}, \texttt{snap\_CA}, \texttt{snap\_TX}, \texttt{snap\_WI}, \texttt{sell\_price}, and \texttt{list\_price} to build features for our machine learning models.

@@

The first model, based on the Cyclic Boosting approach described above, is used to predict the mean of an assumed negative binomial distribution, and we use the following variables as features: categorical variables for \texttt{store\_id} and \texttt{item\_id}, several derived variables that are constructed from the time-series of the sales records describing trend and seasonality (days since beginning of 2013 as linear trend as well as day of week, day of year, month, and week of month), time windows around the events given in the data set (7 days before until 3 days after for Christmas and Easter, and 3 days before until 1 day after for all other events like New Year or Thanksgiving), a flag denoting a promotion, and the ratio of reduced (\texttt{sell\_price}) and normal price (\texttt{list\_price}). We also include various two-dimensional combinations of these features. In these cases, one of the two dimensions is either \texttt{store\_id} or \texttt{item\_id}, allowing the machine learning model to learn characteristics of individual locations and products.

Unlike most state-of-the-art time series forecasting methods, we do not include lagged target information, for example via stacking of exponentially weighted moving average features, in our model. The reason for this is that including such information makes the learning of exogenous effects, e.g. promotions or events, much harder, as the model tends to rely mainly on temporal confounding. Omitting these kind of variables improves the capability of the machine learning model to learn causal dependencies, which in turn improves the explainability of the model as well as the quality of the forecasts for mid- to long-term predictions and rare events. In order to capture recent trends that are not reflected in the exogenous features of the model, we apply an individual residual correction on each of the predictions of the machine learning model, which accounts for deviations between the exponentially weighted moving average (with a recursive smoothing factor of $0.15$) of the predictions and targets of each product-location combination over the corresponding past. To reflect a realistic replenishment scenario, we use a prediction horizon of two days for our example here, i.e. a target lag of two days for the training.

\noindent
Just to give a rough verification for the accuracy of the mean predictions, we report the MAD and MSE averaged over the full used data set in the test period to be $1.65$ and $10.15$, respectively, while the average of the target, i.e. the sales, is $3.28$. \fig \ref{fig:mean_prediction} shows the time series of both predictions and sales summed over all 100 products and 10 stores during the test period.

@@

In this model focusing on the variance, we use the same set of features as for the mean model described above in sec. \ref{sec:example_mean}, except for dropping the two-dimensional combinations including individual event features. An example for the resulting PDF and CDF predictions for item \texttt{FOODS\_3\_586} in store \texttt{WI\_1} on 2016-05-22 is shown in \fig \ref{fig:pdf_example}.

@@

\fig \ref{fig:cdf_demand} shows the histogram of CDF observations according to the method described in sec. \ref{sec:cdf_histo} for all product-location-day combinations in the test period. As benchmark, we compare the outcome of our negative binomial model to a simpler Poisson assumption, which has only a single model parameter, the mean. Using the same mean predictions for both negative binomial and Poisson model, the negative binomial PDF predictions are much closer to the uniform distribution, which we expect for optimal PDF predictions, than the Poisson PDF predictions, showing the effectiveness of our variance estimation. The only significant deviation of the negative binomial histogram from the uniform distribution can be found in the last bins of CDF values close to $1$. As can be seen when excluding samples with mean predictions lower than $1.0$, this deviation stems from slow-sellers, which are prone to overdispersion.

@@

\fig \ref{fig:invquant_mean} and \fig \ref{fig:invquant_dayofweek} show quantile profile plots for different variables on the x-axis, namely mean predictions and day of week, respectively. All product-location-day combinations in the test period are used to generate the statistics in the plots. It can be seen that the different weekdays (from Monday as 0 to Sunday as 6) show slightly different patterns and that there are larger deviations for higher mean predictions (with fewer samples though).

@@

The quantitative results for the CDF accuracies of our PDF predictions for the different metrics described in sec. \ref{sec:cdf_acc}, calculated over all product-location-day combinations in the test period, can be found in \tab \ref{tab:cdf:acc}. As benchmark, we compare these to the results of a Poisson model assumption needing only the mean as single parameter. Our negative binomial PDF predictions show a significant improvement over the simpler Poisson model, which uses the same mean predictions, for each of the metrics.

\begin{table}[h!]
\begin{center}
\caption{CDF accuracies for negative binomial and Poisson PDF predictions for different metrics calculated over all product-location-day combinations in the test period.}
\label{tab:cdf:acc}
\begin{tabular}{c|c|c}
 & \textbf{NBD} & \textbf{Poisson} \\
\hline
\textbf{EMD} & 0.965 & 0.852 \\
\textbf{KL\_2} & 0.995 & 0.933 \\
\textbf{KL\_e} & 0.997 & 0.954 \\
\textbf{JSD\_2} & 0.999 & 0.982 \\
\textbf{JSD\_e} & 0.999 & 0.987
\end{tabular}
\end{center}
\end{table}

\section{Conclusion}

We have shown how to use two subsequent machine learning models for mean and variance estimation together with a negative binomial model assumption to come up with individual PDF predictions. This setup is especially useful for retail demand forecasting, where the true demand follows a negative binomial distribution quite closely. Compared to a model-free approach like quantile regression, the distributional assumption therefore drastically reduces the uncertainty of the resulting predictions, which are, by using Cyclic Boosting as underlying machine learning algorithm, fully explainable on the individual level.

Furthermore, we have presented new qualitative and quantitative methods for evaluating predictions in form of full PDFs. For qualitative evaluation, it is important to check the full PDF, especially its tails that are often crucial for subsequent decision making, as well as investigate aggregations of individual PDFs (to reduce the uncertainty of the evaluation) dependent on specific variables, and we have proposed a novel profile approach called quantile profile plot for this. For quantitative evaluation, it is always desirable to have a single number to compare different models in terms of accuracy, and we have suggested to use the deviance between the CDF histogram of the predicted PDFs and the uniform distribution to compare PDF accuracies.

>>>>

\newcommand{\fig}{Fig.}
\newcommand{\eqn}{Eqn.}
\newcommand{\tab}{Tab.}
\newcommand{\wrt}{w.r.t.}
\newcommand{\etal}{ {\em et al.}}

@@

In detail, the following meta-algorithm describes how the model parameters $f^k_j$ are obtained from the training data:
\begin{enumerate}
\item{Calculate the global average $\mu$ from all observed $y$ across all bins $k$ and features $j$.}
\item{Initialize the factors $f^k_j \leftarrow 1$}
\item{Cyclically iterate through features $j = 1,...,p $ and calculate in turn for each bin $k$ the partial factors $g$ and corresponding aggregated factors $f$, where indices $t$ (current iteration) and $\tau$ (current or preceding iteration) refer to iterations of full feature cycles as the training of the algorithm progresses:
\begin{equation} \label{factors}
g^k_{j,t} = \frac{\sum \limits_{x_{j,i} \in b^k_j} y_i}{\sum \limits_{x_{j,i} \in b^k_j} \hat{y}_{i,\tau}}\;\; \mathrm{where} \; \; f^k_{j,t} = \prod \limits_{s=1}^t g^k_{j,s}
\end{equation}
Here,  $g$ is a factor that is multiplied to $f_{t-1}$ in each iteration. The current prediction, $\hat{y}_\tau$, is calculated according to \eqn \eqref{eqn:cb} with the current values of the aggregated factors $f$:
\begin{equation} \label{factors3}
\hat{y}_{i,\tau} = \mu \cdot \prod \limits_{j=1}^p f^k_{j,\tau}
\end{equation}
To be precise, the determination of $g^k_{j,t}$ for a specific feature $j$ uses $f^k_{j,t-1}$ in the calculation of $\hat{y}$. For the factors of all other features, the newest available values are used, i.e., depending on the sequence of features in the algorithm, either from the current ($\tau=t$) or the preceding iteration ($\tau=t-1$).}
\item{Quit when stopping criteria, e.g. the maximum number of iterations or no further improvement of an error metric such as the mean absolute deviation (MAD) or mean squared error (MSE), are met at the end of a full feature cycle.}
\end{enumerate}

@@

In case of discrete probability functions, such as the negative binomial function, the same argument still holds, but the definition of the inverse quantile function is replaced by the generalized inverse: $F^{-1}(y) = \mathrm{\inf \left \{x : F(x)>y\right  \} }$ for $y \in [0,1]$, see e.g. \cite[p. 54]{casella2002statistical}. In order to obtain a uniform distribution for discrete PDFs that is comparable to the case of continuous distributions, the histogram holding the values of the CDF is filled using random numbers according to the intervals of the CDF. For example, if the sales of zero items accounts for 75\% of the observed sales distribution for this item, the value of the CDF function that is used to fill the histogram in case of zero actual sales is randomly chosen in the interval $[0, 0.75]$. Proceeding similarly for all other observed values, with the intervals from which to randomly choose values to fill in the histogram defined by the CDF values of the corresponding discrete sales value and the one below (e.g. for 3 actual sales: random pick between discrete CDF values for 2 and 3), the resulting histogram of CDF values should again be uniform as in the case of a continuous PDF.

@@

\begin{figure}
\begin{center}
\includegraphics[width=2.5cm]{../figures/CDFHistos_uniform}
\includegraphics[width=2.5cm]{../figures/CDFHistos_broad}
\includegraphics[width=2.5cm]{../figures/CDFHistos_narrow}
\includegraphics[width=2.5cm]{../figures/CDFHistos_over}
\includegraphics[width=2.5cm]{../figures/CDFHistos_under}
\caption{\label{fig:cdf_histos} Quantile distribution for different cases of estimating the full probability distribution compared to the expected distribution:
correct prediction (``uniform''), variance overestimated (``broad''), variance underestimated (``narrow''), mean overestimated (``over''), mean underestimated (``under'')}
\end{center}
\end{figure}

@@

Then we compare the actual observed sales value (corrected for censored data if necessary) to different quantiles of the corresponding predicted distribution for each data record and average over a larger data sample. For example, if we wanted to check that the median of the distribution, corresponding to the $0.5$ quantile, is predicted correctly by the machine learning model, we would compare the quantile value $0.5$ to the ratio of quantile values (again randomly chosen from the corresponding range of CDF values for discrete target values, as described in sec. \ref{sec:cdf_histo}) of observed sales records being lower/higher than $0.5$. In other words, in case of the median, 50\% of the ex post observed target values should be observed below the median of the corresponding individual predicted PDF and 50\% above.

@@

In summary, this approach has two major benefits compared to the method discussed in sec. \ref{sec:cdf_histo}: First, by explicitly visualizing several different quantiles, the quantile profile plot reveals which part of the predicted PDF, such as the tails of the probability distribution, are particularly problematic. Second, by showing the dependency from the (arbitrary) variable on the x-axis, the quantile profile plot reveals deviations of the predicted PDF from the actuals for different parts, e.g. specific categories, of that variable. Two examples for this can be found in Figs. \ref{fig:invquant_mean} and \ref{fig:invquant_dayofweek} in the next section.

@@

In the following, we describe how to use the approach outlined above in a practical setting. We use a public dataset obtained from a Kaggle online competition focusing in estimating unit sales of Walmart retail goods \cite{kaggle_data} for individual SKUs for specific stores on specific days. For each demand forecast, Cyclic Boosting is used to predict the full probability density distribution of the expected demand at a granularity of (SKU, store, day) and use the methods described in Sec. \ref{sec:pdfEvaluation} to evaluate the quality of the individual forecasts. Each data record corresponding to an observed sales record is described by the following fields: the identifier of an individual store store (\texttt{store\_id}), the product identifier (\texttt{item\_id}) as well as the date. The target $y$, that we need to predict, is the number of sales of a given product in a given store on a specific day, denoted by \texttt{sales}.

For our experiments, we use data from 2013-01-01 to 2016-05-22, that describe the sales of 100 different products (\texttt{FOODS\_3\_500}, ..., \texttt{FOODS\_3\_599}) of the department \texttt{FOODS\_3} in 10 stores.  All data before 2016 are used as the training data and the data from 2016 are used as an independent test or validation set. Besides the fields used to identify an individual sales record and the corresponding observed sales value, namely \texttt{item\_id}, \texttt{store\_id}, \texttt{date}, \texttt{sales}, we also use the fields \texttt{event\_name\_1}, \texttt{event\_type\_1}, \texttt{snap\_CA}, \texttt{snap\_TX}, \texttt{snap\_WI}, \texttt{sell\_price}, and \texttt{list\_price} in the forecasts and multiple features are built from these variables that are then used in the machine learning models.

@@

As discussed earlier, we assume that each individual sale can be described by a Poisson-like process and we assume a negative binomial distribution to model the individual probability distribution of each sales event. As a first step, we use Cyclic Boosting to predict the mean of the distribution.

\noindent
This model uses the following variables as features: categorical variables for \texttt{store\_id} and \texttt{item\_id}, several derived variables that are constructed from the time-series of the sales records describing trend and seasonality (days since beginning of 2013 as linear trend as well as day of week, day of year, month, and week of month), time windows around the events given in the data set (7 days before until 3 days after for Christmas and Easter, and 3 days before until 1 day after for all other events like New Year or Thanksgiving), a flag denoting a promotion, and the ratio of reduced (\texttt{sell\_price}) and normal price (\texttt{list\_price}). We also include various two-dimensional combinations of these features. In these cases, one of the two dimensions is either \texttt{store\_id} or \texttt{item\_id}, allowing the machine learning model to learn characteristics of individual locations and products.

Unlike most state-of-the-art time series forecasting methods, we do not include lagged target information, for example via stacking of exponentially weighted moving average features, in our model. Although common in practice, including such variables makes the learning of exogenous effects, such as product promotions or the occurrence of special events, much harder. This is because when those variables are included, machine learning models tend to rely mainly on temporal confounding. Therefore, omitting these kind of variables improves the capability of the machine learning model to learn causal dependencies, which in turn improves the explainability of the model as well as the quality of the forecasts for mid- to long-term predictions and rare events. In order to capture recent trends that are not reflected in the exogenous features of the model, we apply an individual residual correction on each of the predictions of the machine learning model, which accounts for deviations between the exponentially weighted moving average (with a recursive smoothing factor of $0.15$) of the predictions and targets of each product-location combination over the corresponding past. We use the model to predict the expected demand two days into the future to reflect a realistic replenishment scenario, meaning that we use a target lag of two days for the training.

\noindent
We use the mean absolute deviation (MAD) as well as the mean squared error (MSE) as two common metrics for the evaluation of point estimates to give a rough estimate of the accuracy of the predicted mean. These metrics do not take the shape of the underlying probability distribution into account, but only compare the predicted mean to the observed number of sales. Using the independent test data, we obtain the following metrics: MAD: $1.65$ and MSE: $10.15$. The mean of the target, i.e. the observed sales, is $3.28$ for this period. \fig \ref{fig:mean_prediction} shows the time series of both predictions and sales summed over all 100 products and 10 stores during the test period.

@@

\noindent
In this model focusing on the variance, we use the same set of features as for the mean model described above in sec. \ref{sec:example_mean}, except for dropping the two-dimensional combinations including individual event features. An example for the resulting PDF and CDF predictions for item \texttt{FOODS\_3\_586} in store \texttt{WI\_1} on 2016-05-22 is shown in \fig \ref{fig:pdf_example}.

@@

\fig \ref{fig:cdf_demand} shows the histogram of CDF observations according to the method described in sec. \ref{sec:cdf_histo} for all product-location-day combinations in the test period. As benchmark, we compare the outcome of our negative binomial model to a simpler Poisson assumption, which has only a single model parameter, the mean. Using the same mean predictions for both negative binomial and Poisson model, the negative binomial PDF predictions are much closer to the uniform distribution, which we expect for optimal PDF predictions, than the Poisson PDF predictions, showing the effectiveness of our variance estimation. The only significant deviation of the negative binomial histogram from the uniform distribution can be found in the last bins of CDF values close to $1$. These cases are due to slow moving articles with a predicted mean lower than $1.0$, i.e. less than one item sold per store per day on average. These items have been removed in the lower part of  \fig \ref{fig:cdf_demand} and the resulting cumulative distribution is flat as expected. In practice, predicting the demand for these kind of items is very challenging as they are prone to over-dispersion and large fluctuations due to the discrete nature of the sales event.

@@

Using the profile plots introduced earlier, the prediction quality of the full predicted probability distribution can be assessed in more detail. \fig \ref{fig:invquant_mean} shows the quantile profile plot using the predicted mean as the $x$-axis of the graph, meaning that the distributions are grouped such that the 10 columns correspond to mean predictions in the intervals $[0.0, 5.0]$, $(5.0, 10.0]$, $(10.0, 15.0]$, $(15.0, 20.0]$, $(20.0, 30.0]$, $(30.0, 40.0]$, $(40.0, 50.0]$, $(50.0, 60.0]$, $(60.0, 80.0]$, $(80.0, 100.0]$ (with mean predictions higher than 100.0 included in the highest interval), while we aggregate over all locations, items, and sales dates. The considered quantile values are 0.1, 0.3, 0.5, 0.7, 0.9, and 0.97. We can see that for mean predictions higher than $80$, our negative binomial model deviates significantly from the expected behaviour, with the shape of the deviations pointing towards a general underprediction (see  \fig \ref{fig:quant_profiles}). In a real-live situation with a live supply chain project for a customer, a more detailed investigation of the root-causes would then start. However, it should be noted that due to this segregation, the statistics in each part of the relevant test sample becomes a limiting factor as well. This plot also illustrates the benefits of using the quantile profile plot, since we have seen that using more conventional approaches, such as \fig \ref{fig:mean_prediction} or even the lower part of \fig \ref{fig:cdf_demand}, the predictions appear reasonable, even when not relying on simple point metrics such as MAD or MSE. It is therefore paramount both to predict the full probability distribution instead of just a point estimate, such as the mean, as well as verifying a number of quantiles for each prediction to assess the quality of the prediction thoroughly. In \fig \ref{fig:invquant_dayofweek}, each column corresponds to a day of the week, using 0 for Mondays, 1 for Tuesdays, etc., and the used quantile values are the same as in \fig \ref{fig:invquant_mean}. Aggregating over all stores, items, and sales dates (independently for each day of the week), we can see that each quantile is predicted relatively well.

@@

The quantitative results for the CDF accuracy of our PDF predictions for the different metrics described in sec. \ref{sec:cdf_acc}, calculated over all product-location-day combinations in the test period, can be found in \tab \ref{tab:cdf_acc}. As benchmark, we again compare against a Poisson model assumption using the same mean predictions. As expected from the qualitative findings in \fig \ref{fig:cdf_demand}, the negative binomial PDF predictions show a significant improvement over the simpler Poisson model.

\begin{table}[h!]
\begin{center}
\caption{CDF accuracy for negative binomial and Poisson PDF predictions for different metrics calculated over all product-location-day combinations in the test period.}
\label{tab:cdf_acc}
\begin{tabular}{c|c|c}
 & \textbf{NBD} & \textbf{Poisson} \\
\hline
\textbf{EMD} & 0.965 & 0.851 \\
\textbf{KL\_2} & 0.995 & 0.933 \\
\textbf{KL\_e} & 0.997 & 0.954 \\
\textbf{JSD\_2} & 0.999 & 0.982 \\
\textbf{JSD\_e} & 0.999 & 0.987
\end{tabular}
\end{center}
\end{table}

\section{Conclusion}
Demand forecasting remains a crucial step in operational planning for retailers. Both from practical and theoretical perspectives, disentangling the forecast of demand from the operational decision making regarding order quantities has potentially significant advantages over an integrated approach using data to predict the resulting order quantities directly. When predicting future demand, both model-free and a model-based approaches can be used, where the model-based approach is generally more robust, as it is rooted in a theoretical understanding of the sales process. Compared to a model-free approach like quantile regression, the distributional assumption can drastically reduce the uncertainty of the resulting predictions. Using the Cyclic Boosting machine learning approach, the full probability density distribution can be predicted in a fully explainable way on the individual level. This allows to extract not only simple point estimates, such as the expected mean demand, but all relevant quantiles of the distribution.

Evaluating these PDF predictions becomes the critical question. Common metrics, such as the mean absolute deviation or mean squared error, only take point estimates into account and are generally not suitable for the evaluation of predicted probability distributions. Furthermore, since the distributions are predicted for individual events, statistical techniques aiming at the comparison of distributions using many events cannot be used in general. Instead, both the histogram of the probability integral transformation as well as quantile profile histograms allow a detailed investigation into the behavior of the predictions. Finally, a quantitative assessment resulting in a single number can be obtained using metrics such as the earth mover distance in a comparison between the histogram of the probability integral transformation and the expected uniform distribution.
